Bioverse: Potentially Observable Exoplanet Biosignature Patterns Under the UV Threshold Hypothesis for the Origin of Life

### 2025-02-05 src/tex/ms.tex
discuss additional mechanisms

\rev{
Planets around M~dwarfs, in particular, may be subject to significant atmospheric loss due to the extended high-luminosity pre-main-sequence phase of their host stars~\citep[e.g.,][]{Luger2015}.
%During this period, extreme X-ray and UV irradiation can drive rapid hydrodynamic escape, potentially stripping a planet of its primordial atmosphere before abiogenesis can occur.
%Even after this early phase, M-dwarf planets remain exposed to intense stellar activity, leading to further erosion of secondary atmospheres if not replenished through volcanic outgassing or other mechanisms.
Recent works~\citep[e.g.,][]{ParkCoy2024,Luque2024} interpret JWST eclipse measurements as growing evidence for the absence of substantial atmospheres on M-dwarf rocky exoplanets.
If these planets indeed lack atmospheres, their habitability would be primarily dictated by the rate of atmospheric escape~\citep[e.g.,][]{Owen2020}.
However, alternative interpretations remain viable: \citet{Ducrot2024} and \citet{Hammond2025} recently demonstrated that current JWST data cannot definitively distinguish between a bare-rock scenario and an atmosphere composed primarily of N$_2$-CO$_2$-H$_2$O.
This underscores the need for future observations and modeling efforts to constrain atmospheric retention and escape processes more robustly.}
...

%For instance, atmospheric escape processes may play a critical role not only in maintaining a planet's atmosphere but also in regulating the planet's water inventory and the availability of volatile elements for prebiotic chemistry.

\rev{While not modeled here, the above additional mechanisms may offer directions for future work.}

>>>>

\rev{
Planets around M~dwarfs, in particular, may be subject to significant atmospheric loss due to the extended high-luminosity pre-main-sequence phase of their host stars~\citep[e.g.,][]{Luger2015}.
%During this period, extreme X-ray and UV irradiation can drive rapid hydrodynamic escape, potentially stripping a planet of its primordial atmosphere before abiogenesis can occur.
%Even after this early phase, M-dwarf planets remain exposed to intense stellar activity, leading to further erosion of secondary atmospheres if not replenished through volcanic outgassing or other mechanisms.
Recent works~\citep[e.g.,][]{ParkCoy2024,Luque2024} interpret JWST eclipse measurements as growing evidence for the absence of substantial atmospheres on M-dwarf rocky exoplanets.
If these planets indeed lack atmospheres, their habitability would be primarily dictated by the rate of atmospheric escape~\citep[e.g.,][]{Owen2020}.
However, alternative interpretations remain viable: \citet{Ducrot2024} and \citet{Hammond2025} recently demonstrated that current JWST data cannot definitively distinguish between a bare-rock scenario and an atmosphere composed primarily of N$_2$-CO$_2$-H$_2$O.
This underscores the need for future observations and modeling efforts to constrain atmospheric retention and escape processes more robustly.}
%For instance, atmospheric escape processes may play a critical role not only in maintaining a planet's atmosphere but also in regulating the planet's water inventory and the availability of volatile elements for prebiotic chemistry.

\rev{Beyond atmospheric escape, internal heating from tidal forces or radioactive decay can extend or constrain the limits of planetary surface habitability~\citep[e.g.,][]{Barnes2013,Oosterloo2021}.
Tidal effects are especially relevant for \gls{HZ} M~dwarf planets, where strong stellar interactions can drive internal heating, loss of water or an atmosphere, or runaway greenhouse conditions.
Tidal locking may also create extreme climate zones, challenging habitability.}
\rev{While not modeled here, the factors outlined above may offer directions for future work.}
